\documentclass[10pt]{article}
\begin{document}
% This is a comment

\section{Basic Text Manipulation}
% {} creates a limited scope
This word is {\Large Large}
But this is not\\
\underline{Underlined Text}\\
\textit{Italic Text}\\
\textbf{Bold Text}\\
\textbf{{\textit{This sentence is both Italic and Bold  }}}
\section{Fonts}
\textrm{Roman Font (default)}\\
\textsf{Sans Serif}\\
\texttt{TypeWriter}\\


\section{Text Alignment}
\subsection{Centered Text}
\begin{center}
Burges bought the lease on the plot of land in 1875. The house was built by the Ashby Brothers, with interior decoration by members of Burges's long-standing team of craftsmen such as Thomas Nicholls and Henry Stacy Marks. By 1878 the house was largely complete, although interior decoration and the designing of numerous items of furniture and metalwork continued until Burges's death in 1881. The house was inherited by his brother-in-law, Richard Popplewell Pullan. It was later sold to Colonel T. H. Minshall and then, in 1933, to Colonel E. R. B. Graham.
\end{center}

\subsection{Left Aligned Text}
\begin{flushleft}
Burges bought the lease on the plot of land in 1875. The house was built by the Ashby Brothers, with interior decoration by members of Burges's long-standing team of craftsmen such as Thomas Nicholls and Henry Stacy Marks. By 1878 the house was largely complete, although interior decoration and the designing of numerous items of furniture and metalwork continued until Burges's death in 1881. The house was inherited by his brother-in-law, Richard Popplewell Pullan. It was later sold to Colonel T. H. Minshall and then, in 1933, to Colonel E. R. B. Graham.
\end{flushleft}

\section{Paragraphs}

This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.This is a Paragraph.

This is another paragraph. It starts a few space right to the previous
paragraph.This is another paragraph. It starts a few space right to the previous paragraph.This is another paragraph. It starts a few space right to the previous paragraph.This is another paragraph. It starts a few space right to the previous paragraph.This is another paragraph. It starts a few space right to the previous paragraph.This is another paragraph. It starts a few space right to the previous paragraph.This is another paragraph. It starts a few space right to the previous paragraph.

This is yet another paragraph. It starts a few space right to the previous paragraph.This is yet another paragraph. It starts a few space right to the previous paragraph.This is yet another paragraph. It starts a few space right to the previous paragraph.This is yet another paragraph. It starts a few space right to the previous paragraph.This is yet another paragraph. It starts a few space right to the previous paragraph.This is yet another paragraph. It starts a few space right to the previous paragraph.

\section{New Lines}
This is a Line.\\
This is another Line.\\\\\\
This is 2 Lines Later.
\end{document}